%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 6CCS3PRJ Final Year Individual Project Report
% luke.day@kcl.ac.uk
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{informatics-report}
\usepackage{color}
\usepackage[square,sort,comma,numbers]{natbib} %References
\usepackage{float}% If comment this, figure moves to Page 2
\usepackage{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Front Matter - project title, name, supervisor name and date
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{6CCS3PRJ Final Year\\\vspace{0.2cm}Orchestrator}
\author{Leonardo Ciocan}
\studentID{1308123}
\supervisor{Jeroen Keppens}

\date{\today}

\abstractFile{FrontMatter/abstract.tex}
\ackFile{FrontMatter/acknowledgements.tex} %Remove line if you do not want acknowledgements

\begin{document}
\createFrontMatter
\doublespacing
\tableofcontents
\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Report Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can write each chapter directly here or in a separate .tex file and use the include command.

\chapter{Introduction}
The rise of technology such as mobile devices has been sudden and unexpected , while many industries have quickly adapted to the changes education is one field where embracing technology is still underway. One of the most striking examples of how technology can improve education is the invention of the printer , which enabled literacy to go from 10\% to 80\% in a matter of 50 years \cite{printing}.

A number of other studies show that introducing technology in a learning environment can have a positive impact \cite{tech} and that there is a international movement to augment learning with technology \cite{tech2}.
Today , we live in a world where every student in developed countries has access to a electronic device - in fact , for subjects such as engineering and computer science , virtually every student has access to such a device \cite{laptop1} \cite{laptop2} . In UK universities in particular , paper handouts are still used in lectures ; their purpose is for the students to be able to test how well they understand the current concept being taught and for teachers to gauge the student's understanding of the subject and adjust their teaching schedule accordingly.

A digital replacement of these handouts has the potential to increase student engagement , minimise the friction of distributing , collecting and analysing data and allow the overall turnaround time for the teaching process to be as small as possible.

\section{Motivation}
Handouts can ask a variety of questions ; they can have images , tables , formatted text and more. If a digital alternative is to replace this , it must be flexible enough to support a variety of question types. Further more , paper handouts allow the user to draw or express their answer in a number of ways  , this can be a disadvantage since the students could write invalid answers ( i.e select two answers in a single answer multiple choice question) however it also provides a lot of flexibility. A digital solution must solve both problems by providing flexible , tailored ways to express the questions and to answer them in a way that is valid and yet allow the user to express their creativity.

To account for this goal , the end product build will be tailored for computer science students. This is to showcase the features of the platform and allow for a focused development cycle that would prove the usefulness of a digital solution for this problem. Part of this tailoring will be a question type that let's students write their own code and have it executed and checked by the system.

The data visualisation part of this project provides a number of ways to explore novel ways to show the aggregated data in ways that is useful to the teacher and is tailored for each question type.

In section \ref{future} (Future work) it will be discussed how the system , once shown to work as intended , can be extended further and be tailored for all the subjects that make up higher education. This is because the project will be developed as a platform and make it so adding question types will be simple.


\section{Existing solutions}
There are some products that have attempted to tackle the teacher - student interaction in the classroom.
One of the most popular is called Socrative \footnote{Socrative \url{http://www.socrative.com/}} , which allows teachers to ask the students quizzes. However the system is very limited and only allows text questions , where the answers can be a choice or piece of text. This is not flexible and rich enough to replace traditional methods , only to agreement them. However , it has been downloaded over 1000000 times just on android \footnote{Socrative on Google Play \url{https://play.google.com/store/apps/details?id=com.socrative.student}} , which shows there is a clear market for such solutions.

Another service that could be potentially a competitor is Moodle \footnote{Moodle \url{https://moodle.org/}} . It is not usually used in classroom settings but it does provide support for making quizzes that the students can answer and the teacher can analyse the questions. However this feature is a minor part of Moodle and it does not provide any of the real time advantages of other solutions , including the one described in this project. Some teachers use this to collect code written by user's and then script a solution to execute and mark the answers - however this is not a good solutions as students get little feedback and the process is not automated.

Overall , one of the goals of this project is to bring together the advantages of all those different solutions in a package that is extensible and yet retains the ability to be easy to use for both students and teachers.

\subsection{Platform}
I have decided to build this project for the web instead of a mobile application for a number of reasons. Since this is meant to be used by a lot of students, it is a requirement that it should be as accessible as possible. Statistically speaking, a web app can reach the most people, especially account for the fact that computing students are the main target audience and they are likely to have laptops with them.
The main disadvantage of making mobile apps is that to build a good native app would mean to focus on one platform (as cross platform solutions are not up to the task for the scope of the project) which would exclude students from the process. The web is a free, universal platform and so it is the perfect medium for this project.
Ideally, fully native mobile apps are further down the roadmap as they provide a better experience and further expand the pool of users that are able to use the application.
The backend part of this project has been built in such a way to allow for easy expansion to other platforms. In fact, the web app could be considered just a consumer of the backend and not being renderer by the server such that another front-end could be used instead without any friction.



\subsection{Objectives}
Because the main target audience is made up of computer savvy student and lecturers, it was possible to take a few liberties with the platform. For example the questions can be written in Markdown, which is something computer scientists are already familiar with from websites such as StackOverflow and Github.
Nevertheless, I aim to make a project that requires minimal guidance as the user interface will be built to be easy and intuitive to operate.

The basic requirements for this project are:
\begin{enumerate}
\item Let teacher create sheets made of a variety of question types
\item 	Allow question types to include rich formatting such as tables and code
\item 	Allow students to subscribe to a lecture such that they may have access to those sheets
\item 	Allow a teacher to create a class and invite students with a link
\item 	Let the teacher decide when a sheet should go “live” and be visible by the students
\item 	Allow the teacher to attach model answers to each question
\item Let the teacher release model answers to the students so they may review their answers
\item 	Monitor the students progress and present it to the teacher in an anonymous way
Allow users to write code to be executed for code questions

\end{enumerate}
\subsection{Report structure}
The next section will be the background which will begin by exploring the keywords or concepts that are related to the project.
It will also analyse and contrast current implementation that attempt to solve the problem described with the project's implementation.

\include{Chapters/Background}
\include{Chapters/Body}
\include{Chapters/DesignSpecification}
\include{Chapters/Implementation}
\include{Chapters/ProfessionalIssues}
\include{Chapters/Evaluation}
\include{Chapters/Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{references}
\addcontentsline{toc}{section}{Bibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\include{Appendices/appendix}
\include{Appendices/UserGuide}
\include{Appendices/SourceCode}
\end{document}
